### 2017-10-30 paper/sections/1_introduction.tex
paper: add code snippets for FS comparison
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\section{Introduction}
ParSplice~\cite{perez:jctc20150parsplice}

>>>>

\section{Introduction}

% What is the problem we are trying to solve
[DESCRIBE PROBLEM WE ARE TRYING TO SOLVE - CUT/PASTE FROM PDSW PAPER]

% What is Mantle
To solve this problem, we integrate Mantle into
ParSplice~\cite{perez:jctc20150parsplice}. Mantle is a dynamic policy engine
that decomposes complicated services into manageable pieces so developers
unfamiliar with a code-base can reason about its behavior. Administrators use
the framework to describe ``when" they want data moved, ``where" they want data
moved, and ``how much" of the data to move.  This abstraction helps developers
unfamiliar with the domain quickly reason about, develop, and deploy new
policies that control temporal and spatial locality. It has already proven to
be a critical control plane for improving file system metadata load
balancing~\cite{sevilla:sc15-mantle} and in this work we show its usefulness in
cache management.

% What are we going to show
We show how Mantle:
\begin{itemize}

  \item decomposes cache management into independent policies, making the
  problem more manageable and facilitating rapid development. We quickly implement
  the ``how much" policy and focus on the ``when" policy for the majority of this paper.

  \item has useful primitives that, while designed for file systems, are
  crucial for effective cache management. This finding shows how the Mantle
  engine generalizes to a different domain and code-base.

  \item can be used to quickly deploy a variety of cache management strategies,
  ranging from basic algorithms and heuristics to statistical models and machine
  learning. This mixing and matching may not outperform a hard-coded solution but
  can more adeptly change to different workloads and hardware.

\end{itemize}

We demonstrate these contributions by changing the input to our molecular
dynamics simulation, which changes the keyspace access patterns.

%First, we implement the ``how much" abstraction as an LRU and then we focus on
%the ``when" abstraction.

%Manageable: abstracts away complexities of the system (pass around to others,
%use different strategies)

### 2017-10-30 paper/sections/4_dynamic-policies.tex
paper: add code snippets for FS comparison
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

\section{Mantle Brains: Tools We Plug In}

@@

@@

We tried looking at system-specific metrics to design policies, like request
rate, unique keys in a sliding window, bandwidth capabilties. For example, we
know that LevelDB cannot handle high IO request rates.

\subsubsection{when: request rate}

\subsubsection{when: Belady's Min}

We tried looking at domain-specific metrics to design policies, like ParSplice
key access locality.

\subsubsection{howmuch: regime detection}
\subsubsection{when: trajectory length goodness}
\subsubsection{howmuch: cache policy from past}

@@

What if we re-provision resource in response to events outside the
application's control, such as a slow Lustre.

>>>>

\section{Mantle Brains: Tools We Plug In to Detect ``when"}

@@

{\it e.g.}, request rate, unique keys in a sliding window, bandwidth
capabilties. For example, we know that LevelDB cannot handle high IO request
rates.

\subsubsection{Request Rate}

\subsubsection{Belady's Min}

{\it e.g.}, ParSplice key access locality.

\subsubsection{Regime Detection}
\subsubsection{Trajectory Length}

@@

@@

What if we re-provision resources in response to events outside the
application's control, such as a slow Lustre.

\subsection{Future work}

How Much: cache policy from past, regime detection

### 2017-10-30 paper/sections/5_file-systems.tex
paper: add code snippets for FS comparison
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

>>>>

The code snippets in Figures~\ref{lua:parsplice} and~\ref{lua:cephfs} are the
policies used in ParSplice and CephFS, respectively.  ParSplice uses policies
to manage its caches and CephFS uses policies to control load balancing, but
they both can be expressed with the Mantle API.  From a high-level the
ParSplice policy trims the cache if the cache reaches a certain size {\it and}
if it has already absorbed the initial burstiness of the workload; the CephFS
policy migrates load if the metadata load is higher than the average load {\it
and} the current load has been overloaded for more than two iterations.

\textbf{Condition for ``Overloaded"} (Fig.~\ref{lua:parsplice}:Line 2;
Fig.~\ref{lua:cephfs}:Line 2) - these lines detect whether the node is
overloaded using the ``load" calculated in the load callback; while the load
calculations and thresholds are different, the actual logic is exactly the
same.  Recall that this decision is made locally because there is no global
scheduler or centralized intelligence.

\textbf{State Persisted Across Decisions} (Fig.~\ref{lua:parsplice}:Lines 5,6;
Fig~\ref{lua:cephfs}:Lines 3,4,10) - these lines use the Mantle API to
write/read state from previous decisions.  For ParSplice, we save a boolean
that indicates whether we have absorbed the workload's initial burstiness. For
CephFS, we save the number of consecutive instances that the server has been
overloaded. We also clear the count (Line 10) if the server is no longer
overloaded. The underlying implementation saves the values to local disk.

\textbf{Condition that Switches Policy} (Fig.~\ref{lua:parsplice}:Line 3;
Fig.~\ref{lua:cephfs}:Line 5) - these lines switch the policies using
information from previous decisions. ParSplice trims its cache once it eclipses
the ``absorb" threshold while CephFS allows balancing when overloaded for more
than two iterations. The persistent state is essential for both of these
policy-switching conditions.

\begin{figure}[tb]
\begin{minted}[linenos]{lua}
local function when()
  if servers[whoami]["load"] > target then
    if servers[whoami]["load"] > absorb_target then
      WRstate(1)
    end
    if RDstate() == 1 then
      return true
    end
  end
  return false
end
\end{minted}
\caption{ParSplice cache management policy.\label{lua:parsplice}}
\end{figure}

\begin{figure}[tb]
\begin{minted}[linenos]{lua}
local function when()
  if servers[whoami]["load"] > target then
    overloaded = RDstate() + 1
    WRstate(overloaded)
    if overloaded > 2 then
      return true
    end
  end
  else then
    WRstate(0)
  end
  return false
end
\end{minted}
\caption{CephFS file system metadta load balancer.\label{lua:cephfs}}
\end{figure}
